Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-15 Paper.tex
Move timestamp to correct position.
Minor correction & clarification.
Update transaction component ordering.
Remove old reference to body.

The function $L_T$ prepares a transaction for being transformed into an RLP-serialised byte array:
\begin{equation}
L_T(T) \equiv \begin{cases}
(T_n, T_v, T_t, T_p, T_g, T_\mathbf{i}, T_w, T_r, T_s) & \text{if} \; T_t = 0\\
(T_n, T_v, T_t, T_p, T_g, T_\mathbf{d}, T_w, T_r, T_s) & \text{otherwise} 
\end{cases}
\end{equation}

Here, we assume all components are interpreted by the RLP as integer values, with the exception of the arbitrary length byte arrays $T_\mathbf{b}$, $T_\mathbf{i}$ and $T_\mathbf{d}$ and the address hash $T_\mathbf{t}$:
\begin{equation}
\begin{array}[t]{lclclc}
T_n \in \mathbb{P} & \wedge & T_v \in \mathbb{P} & \wedge & T_p \in \mathbb{P} & \wedge \\
T_g \in \mathbb{P} & \wedge & T_w \in \mathbb{P} & \wedge & T_r \in \mathbb{P} & \wedge \\
T_s \in \mathbb{P} & \wedge & T_\mathbf{d} \in \mathbb{B} & \wedge & T_\mathbf{i} \in \mathbb{B} & \wedge \\
T_t \in \mathbb{B}_{20} &&&&
\end{array}
\end{equation}

@@

The function $L_B$ and $L_H$ are the preparation functions for a block and block header respectively. Much like the transaction receipt preparation function $L_R$, we assert the types and order of the structure for when the RLP transformation is required:
\begin{eqnarray}
\quad L_H(H) & \equiv & (\begin{array}[t]{l}H_p, H_u, H_b, H_r, H_t, H_d, H_s,\\ H_i, H_m, H_l, H_u, H_x, H_n \; )\end{array} \\
\quad L_B(B) & \equiv & \big( L_H(B_H), L_R^*(B_\mathbf{R}), L_H^*(B_\mathbf{U}) \big)
\end{eqnarray}

@@

Where $0_{256}$ refers to the parent and state and transaction root hashes, a 256-bit hash which is all zeroes; $0_{160}$ refers to the coinbase address, a 160-bit hash which is all zeroes; $2^{22}$ refers to the difficulty; 0 refers to the timestamp (the Unix epoch); $()$ refers to the extradata and the sequences of both uncles and transactions, all empty. $\mathtt{\tiny SHA3}\big( (42) \big)$ refers to the SHA3 hash of a byte array of length one whose first and only byte is of value 42. $\mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big)$ values refer to the hashes of the transaction and uncle lists in RLP, both empty.

>>>>

The function $L_T$ prepares a transaction for being transformed into an RLP-serialised byte array:
\begin{equation}
L_T(T) \equiv \begin{cases}
(T_n, T_p, T_g, T_t, T_v, T_\mathbf{i}, T_w, T_r, T_s) & \text{if} \; T_t = 0\\
(T_n, T_p, T_g, T_t, T_v, T_\mathbf{d}, T_w, T_r, T_s) & \text{otherwise} 
\end{cases}
\end{equation}

Here, we assume all components are interpreted by the RLP as integer values, with the exception of the arbitrary length byte arrays $T_\mathbf{i}$ and $T_\mathbf{d}$ and the address hash $T_\mathbf{t}$:
\begin{equation}
\begin{array}[t]{lclclc}
T_n \in \mathbb{P} & \wedge & T_v \in \mathbb{P} & \wedge & T_p \in \mathbb{P} & \wedge \\
T_g \in \mathbb{P} & \wedge & T_w \in \mathbb{P} & \wedge & T_r \in \mathbb{P} & \wedge \\
T_s \in \mathbb{P} & \wedge & T_\mathbf{d} \in \mathbb{B} & \wedge & T_\mathbf{i} \in \mathbb{B} & \wedge \\
T_t \in \mathbb{B}_{20} &&&&
\end{array}
\end{equation}

@@

The function $L_B$ and $L_H$ are the preparation functions for a block and block header respectively. Much like the transaction receipt preparation function $L_R$, we assert the types and order of the structure for when the RLP transformation is required:
\begin{eqnarray}
\quad L_H(H) & \equiv & (\begin{array}[t]{l}H_p, H_u, H_b, H_r, H_t, H_d,\\ H_i, H_m, H_l, H_u, H_s, H_x, H_n \; )\end{array} \\
\quad L_B(B) & \equiv & \big( L_H(B_H), L_R^*(B_\mathbf{R}), L_H^*(B_\mathbf{U}) \big)
\end{eqnarray}

@@

Where $0_{256}$ refers to the parent and state and transaction root hashes, a 256-bit hash which is all zeroes; $0_{160}$ refers to the coinbase address, a 160-bit hash which is all zeroes; $2^{22}$ refers to the difficulty; 0 refers to the timestamp (the Unix epoch); $()$ refers to the extradata and the sequences of both uncles and transactions, all empty. $\mathtt{\tiny SHA3}\big( (42) \big)$ refers to the SHA3 hash of a byte array of length one whose first and only byte is of value 42. $\mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big)$ value refers to the hash of the uncle lists in RLP, both empty lists.
